\documentclass{article}

\usepackage{geometry}
\usepackage{hyperref}

\title {Khidmat: Bagh-e-Sakina}

\author{
  Ali Asghar Yousuf\\ ay06993
  \and
  Muhammad Azeem Haider\\ mh06858
  \and
  Mohammad Shahid Mahmood\\ mm06600
  \and
  Syed Ibrahim Ali Haider\\ sh06869
}
\date{\today}  

\begin{document}
\maketitle

% Use first person plural (we, us) even if you did the Khidmat individually.

% An introduction of the project, no more than 2 sentences. Provide the highest level of detail only. Other details will come later.

% Typically, "This project is to <short description of porject> for/at <client>."
The objective of this project is to develop an android mobile application that will digitalize an activity book designed to enhance student engagement and growth through interactive learning experiences for \textit{Bagh-e-Sakina}.

\vspace{1em}

% About the client.
Bagh-e-Sakina is a social enterprise deeply committed to ensuring that every child is granted the fundamental rights and opportunities essential for their overall well-being. With children at the core of its mission, Bagh-e-Sakina develops and implements initiatives aimed at empowering and uplifting them. The organization’s focus is on providing children with the resources, care, and support necessary to secure a brighter and more promising future. Through its unwavering dedication, Bagh-e-Sakina strives to make a lasting, positive impact on the lives of children, ensuring they are at the heart of all its efforts.

\vspace{1em}

% About the project.
The team at Bagh-e-Sakina created an activity book with the purpose of engaging children with healthy activities and mindset. The activity book is a collection of activities ranging from describing your favourite hobbies to drawing things you love. The activities are designed to enhance student engagement, growth, and well-being. The purpose of this project is to develop an android mobile application that will digitalize the activity book and make it more accessible to distribute this activity book to different students. This will allow the students to engage with the activities in a more interactive and engaging way.

\vspace{1em}

% About the plan of work.
We will work part time remotely under the supervision of the Bagh-e-Sakina team. The goal is to develop, test, and deploy a fully working mobile application by the end of our Khidmat.

% Copy-paste this section with necessary modifcations for each week.

\newpage % Start the report for each week on a new page.
\section*{Month 1: February, 2024}

% A summary, maximum 2 sentences, of this week's activities.
We had our first meeting with the Bagh-e-Sakina team in February to understand the requirements and their expectations of the project. This led to us creating a plan for the development of the application and the writing down the proposal for the project.

\vspace{1em}

\noindent \begin{tabular}{|l|l|l|l|}
  \hline
  Item & Activity     & Time  & ID \\ \hline
  1    & Meeting with Bagh-e-Sakina team & 2 hours  & ay06993, mh06858, mm06600, sh06869 \\ \hline
  2    & Proposal     & 5 hours & mh06858 \\ \hline
\end{tabular}

\vspace{1em}

\noindent The total time spent on Khidmat this month is as follows.

\vspace{1em}

\noindent \begin{tabular}{|l|l|}
  \hline
  ID      & Total Hours \\ \hline
  ay06993 & 2 hours     \\ \hline
  mh06858 & 7 hours     \\ \hline
  mm06600 & 2 hours     \\ \hline
  sh06869 & 2 hours     \\ \hline
\end{tabular}

\newpage % Start the report for each week on a new page.
\section*{Month 2: March, 2024}

We spent this month further clarifying the requirements with the Bagh-e-Sakina team. We started working on the design and high-fidelity wireframes for the application as well. 

\vspace{1em}

\noindent \begin{tabular}{|l|l|l|l|}
  \hline
  Item & Activity & Time   & ID                        \\\hline
  1    & Meeting with Bagh-e-Sakina team & 2 hours   & mh06858, mm06600, sh06869 \\\hline
  2    & Wireframes   & 10 hours & mh06858, sh06860          \\\hline
\end{tabular}

\vspace{1em}

\noindent The total time spent on Khidmat this month is as follows.

\vspace{1em}

\noindent \begin{tabular}{|l|l|}
  \hline
  ID      & Total Hours \\ \hline
  ay06993 & 0 hours     \\ \hline
  mh06858 & 12 hours    \\ \hline
  mm06600 & 2 hours     \\ \hline
  sh06869 & 12 hours    \\ \hline
\end{tabular}

\newpage % Start the report for each week on a new page.
\section*{Month 3: April, 2024}

We spent this month meeting with the Bagh-e-Sakina team to finalize the wireframes and design of the application. We also started working on the frontend development of the application.

\vspace{1em}

\noindent \begin{tabular}{|l|l|l|l|}
  \hline
  Item & Activity & Time & ID \\ \hline
  1 & Meeting with Bagh-e-Sakina team  & 3 hours & ay06993, mh06858, mm06600, sh06869 \\ \hline
  2 & Wireframes & 5 hours & mh06858, sh06860 \\ \hline
  3 & Initial app setup & 8 hours & mh06858, ay06993 \\ \hline
\end{tabular}

\vspace{1em}

\noindent The total time spent on the Khidmat this month is as follows.

\vspace{1em}

\noindent \begin{tabular}{|l|l|} \hline
  ID & Total Hours \\ \hline
  ay06993 & 11 hours \\ \hline
  mh06858 & 14 hours \\ \hline
  mm06600 & 3 hours \\ \hline
  sh06869 & 8 hours \\ \hline
\end{tabular}

\newpage % Start the report for each week on a new page.
% Add a note with a * to indicate no work was done in April.
\noindent * No updates for \textbf{May 2024} due to the end-of-semester workload, including Kaavish.
\section*{Month 5: June, 2024}

% A summary, maximum 2 sentences, of this week's activities.
We spent this month meeting with the Bagh-e-Sakina team to gather materials for the application such as the logos and assets for the activity book. We also worked on the development of the application and reporting our progress to the Bagh-e-Sakina team. 

\vspace{1em}

\noindent \begin{tabular}{|l|l|l|l|}
  \hline
  Item & Activity & Time   & ID \\ \hline
  1 & Meeting with Bagh-e-Sakina team & 3 hours & ay06993, mh06858, mm06600, sh06869 \\ \hline
  2 & Managing assets from the .AI file & 3 hours & mm06600 \\ \hline
  3 & Codebase \& environment setup & 2 hours  & mh06858, mm06600, sh06869 \\ \hline
  4 & Auth \& Firestore setup & 7 hours & ay06993 \\ \hline
  5 & Frontend development & 3 hours & mh06858, mm06600, sh06869 \\ \hline
\end{tabular}

\vspace{1em}

\noindent The total time spent on the Khidmat this month is as follows.

\vspace{1em}

\noindent \begin{tabular}{|l|l|}
  \hline
  ID & Total Hours \\\hline
  ay06993 & 10 hours \\ \hline
  mh06858 & 8 hours  \\ \hline
  mm06600 & 9 hours \\ \hline
  sh06869 & 8 hours \\ \hline
\end{tabular}

% Copy-paste this section with necessary modifcations for each week.
\newpage % Start the report for each week on a new page.
\section*{Month 6: July, 2024}

% A summary, maximum 2 sentences, of this week's activities.
We spent this month meeting with the Bagh-e-Sakina team to gather materials for the application. We also worked on the development of the application.

\vspace{1em}

\noindent \begin{tabular}{|l|l|l|l|}
  \hline
  Item & Activity & Time & ID \\ \hline
  1    & Frontend development & 8 hours  & mh06858 \\ \hline
\end{tabular}

\vspace{1em}

\noindent The total time spent on the Khidmat this month is as follows.

\vspace{1em}

\noindent \begin{tabular}{|l|l|}
  \hline
  ID      & Total Hours \\\hline
  mh06858 & 8 hours    \\\hline
\end{tabular}

\newpage
\section*{Month 7: August, 2024}

% A summary, maximum 2 sentences, of this week's activities.
We spent this month completing the development and testing of the application and reporting it to the Bagh-e-Sakina team through meetings on separate occasions. 

\vspace{1em}

\noindent \begin{tabular}{|l|l|l|l|}
  \hline
  Item & Activity & Time & ID \\ \hline
  1 & Meeting with Bagh-e-Sakina team & 3 hours & ay06993, mh06858, mm06600, sh06869 \\ \hline
  2 & Frontend development & 7 hours  & mh06858 \\ \hline
  3 & Fixing glitches and errors in the application & 5 hours  & ay06993, mm06600, sh06869 \\ \hline
  4 & Authentication and backend development & 5 hours & mh06858 \\ \hline
  5 & Testing the application & 2 hours & mh06858, ay06993, mm06600, sh06869 \\ \hline

\end{tabular}

\vspace{1em}

\noindent The total time spent on the Khidmat this month is as follows.

\vspace{1em}

\noindent \begin{tabular}{|l|l|}
  \hline
  ID & Total Hours \\\hline
  ay06993 & 10 hours \\ \hline
  mh06858 & 17 hours  \\ \hline
  mm06600 & 10 hours \\ \hline
  sh06869 & 10 hours \\ \hline
\end{tabular}

\newpage

\section*{Conclusion}

% Remind the reader about the project. Summarise your activities over the course of the project.
The project involved building an android mobile application for Bagh-e-Sakina for their activity book and digitizing it. We planned the entire application from building the wireframes to the development of the application in its entirety. The application was then tested individually to ensure its smooth working, 

\newpage
\thispagestyle{empty}
% Show your external supervisor your report, especially the weekly upates; have them sign a printed copy of this page; scan the signed page; and include the scanned page in this document as an image.

\begin{center}
  {\Large\bf Khidmat Completion Form}\\[5pt]
  \small To be completed by the external supervisor.
\end{center}
\bigskip

\noindent{\it Please use the space below to provide any comments you may have on the students' performance, the Khidmat program, or any other feedback you want to share with Habib University's Khidmat committee. We can also be reached at \href{mailto:khidmat@sse.habib.edu.pk}{khidmat@sse.habib.edu.pk}.}
\vfill

\begin{center}
  \rule{.8\textwidth}{.5pt}
\end{center}
\medskip

% Insert your name below.

I hereby certify that I supervised Ali Asghar Yousuf, Muhammad Azeem Haider,
Mohammad Shahid Mahmood and Syed Ibrahim Ali Haider for the Khidmat described
in this report. Furthermore, that I have read and agree with the weekly updates
included in this report. My signature below marks the successful completion of
the work undertaken for the Khidmat.\\ \bigskip \bigskip

\noindent\begin{tabular}{@{}p{.6\textwidth}@{\hspace{.1\textwidth}}p{.3\textwidth}}
  \hrulefill         & \hrulefill        \\
  Name and signature & Location and date
\end{tabular}

\end{document}